---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(DBI)
library(RSQLite)
library(ggplot2)
db = dbConnect(SQLite(), "lahman2013.sqlite")
dbListTables(db)
lapply(dbListTables(db), function(tbl) dbListFields(db, tbl))
options("scipen" = 10)
options()$scipen
```

1.
```{r}
P = dbGetQuery(db, "SELECT MIN(yearID), MAX(yearID) FROM Appearances")
P
D = dbGetQuery(db, "SELECT DISTINCT yearID FROM Appearances")
nrow(D)
```
2.
```{r}
Playernum = dbGetQuery(db, "SELECT COUNT(DISTINCT playerID) FROM Master")
tail(Playernum)  ##numbers of players
M2 = dbGetQuery(db, "SELECT COUNT(DISTINCT playerID) FROM Managers")
M2  ##numbers if manager
```
3
```{r}
M1 = dbGetQuery(db, "SELECT COUNT(DISTINCT Master.playerID) FROM Master
                       INNER JOIN Managers on Master.playerID = Managers.playerID")
M1
plymanager = dbGetQuery(db, "SELECT COUNT(DISTINCT playerID) FROM Managers WHERE plyrMgr = 'Y'")
plymanager
```

4.
```{r}
app = dbGetQuery(db, "SELECT COUNT (DISTINCT playerID), yearID FROM Appearances
                 WHERE yearID BETWEEN 2000 AND 2013
                 GROUP BY yearID")  ##number of players from 2000 to 2013
tail(app)
Teamember = dbGetQuery(db, "SELECT COUNT(playerID), teamID FROM Appearances
                       GROUP BY teamID")
tail(Teamember)
```

5
```{r}
Win2010 = dbGetQuery(db, "SELECT name, yearID, WSWin, lgID AS League, divID AS division  FROM Teams
                 WHERE yearID = 2010 AND WSWin IS 'Y'")
nrow(Win2010)
tail(Win2010)
```
6
```{r}
Lost = dbGetQuery(db, "SELECT name, yearID, WSWin, lgID AS League, divID AS division FROM Teams
                WHERE WSWin IS 'N'")
nrow(Lost)
tail(Lost)
```

7
```{r}
winners = dbGetQuery(db, "SELECT name, yearID, WSWin, lgID AS League, divID AS division FROM Teams
                WHERE WSWin IS 'Y'")
tail(winners)
```
8
```{r}
winandlost = dbGetQuery(db, "SELECT SeriesPost.yearID, T1.teamID, T1.name, T1.lgID AS League, T1.divID AS division,
                    T2.teamID, T2.name, T2.lgID AS League, T2.divID AS division, losses as 'Lost Team Won'
                    FROM SeriesPost
                    INNER JOIN Teams AS T1
                    INNER JOIN Teams AS T2
                    on SeriesPost.teamIDwinner = T1.teamID AND SeriesPost.teamIDloser = T2.teamID AND                                   SeriesPost.yearID = T1.yearID AND SeriesPost.yearID = T2.yearID
                    WHERE round = 'WS' 
                    ORDER BY T1.yearID DESC
                    LIMIT 3")


tail(winandlost)
```
9
```{r}
WinandWS = dbGetQuery(db, "SELECT yearID, name, W as Wins, WSWin as 'WinsOrNot' FROM Teams ORDER BY yearID ")
WinandWS = na.omit(WinandWS)
summary(glm(data = WinandWS, as.factor(WinsOrNot) ~ Wins,family = "binomial"))
```
10
```{r}
Salary = dbGetQuery(db,"SELECT yearID, salary, Master.* FROM Salaries INNER JOIN Master
                    on Salaries.playerID = Master.playerID
                    ORDER BY salary DESC
                    LIMIT 10")
Salary
```
11
```{r}
salary2010 = dbGetQuery(db,"SELECT teamID, SUM(salary) FROM Salaries
                        WHERE yearID = 2010
                        GROUP BY teamID")
tail(salary2010)
salaryall = dbGetQuery(db,"SELECT teamID, SUM(salary) AS sumsalary, yearID FROM Salaries
                        GROUP BY teamID, yearID")
tail(salaryall)
ggplot(data = salaryall, aes(x = as.factor(yearID), y = sumsalary, group = teamID)) + geom_line(aes(col = teamID)) + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + labs(x = "Years", y = "Salary")
```

14.
```{r}
HRnum = dbGetQuery(db, "SELECT playerID, yearID, MAX(HR) AS HR FROM Batting GROUP BY yearID  ORDER BY HR DESC")
head(HRnum)
```

15
```{r}
HRnum1 = dbGetQuery(db, "SELECT playerID, yearID, SUM(HR) AS HR FROM Batting GROUP BY yearID")
plot(HRnum1$yearID, HRnum1$HR)
```

16
```{r}
sal_vs_run = dbGetQuery(db, "SELECT Batting.yearID, Batting.playerID, HR, salary FROM Batting 
                        INNER JOIN Salaries
                        ON Batting.playerID = Salaries.playerID AND Batting.yearID = Salaries.yearID
                        WHERE Batting.yearID BETWEEN 2010 AND 2013
                        ORDER BY Batting.playerID")

ggplot(data = na.omit(sal_vs_run), aes(x = HR, y = salary)) + geom_point(aes(col = yearID)) + geom_smooth()
```

17
```{r}
park = dbGetQuery(db, "SELECT yearID, park, SUM(HR) AS HR FROM Teams GROUP BY park")
plot(park$HR)
park[park$HR > 10000,]
```


20
```{r}
Start =  dbGetQuery(db, "SELECT yearID, SUM(G) AS StintGames
                    FROM Pitching WHERE stint = 1
                    GROUP BY yearID
                    ORDER BY yearID")
Game =  dbGetQuery(db, "SELECT yearID, SUM(G) AS Games
                    FROM Pitching GROUP BY yearID
                    ORDER BY yearID")
S = data.frame(Year = Start$yearID, Games = Start$StintGames, Stint = rep("1", nrow(Start)))
G = data.frame(Year = Game$yearID, Games = Game$Games, Stint = rep("all", nrow(Game)))
ALL_DATA = rbind(S,G)
ALL_DATA
ggplot(data=ALL_DATA, aes(x=Year, y=Games, fill = Stint)) + geom_bar(stat="identity", position=position_dodge()) + scale_fill_brewer(palette="Paired") + scale_fill_manual(values=c('violet','royalblue4'))